Creating the ``r params$package_name`` R package

### 2025-07-23 create-FSHybridPLS.Rmd
are_all_gram_matrices_identical

>>>>

```{r}
#' Check if all matrices in a list are identical (with tolerance for numeric comparison)
#'
#' This function iterates through a list of matrices and checks if all subsequent
#' matrices are numerically identical to the first matrix in the list.
#' It uses `all.equal` for robust comparison of numeric matrices, which accounts
#' for small floating-point differences.
#'
#' @param gram_list A list of matrices.
#' @param tolerance A numeric tolerance for comparing floating-point numbers.
#'                  Defaults to `sqrt(.Machine$double.eps)`.
#' @return A logical value: `TRUE` if all matrices are identical, `FALSE` otherwise.
#' @export
are_all_gram_matrices_identical <- function(gram_list, tolerance = sqrt(.Machine$double.eps)) {
  # Handle edge cases: empty list or list with a single matrix
  if (length(gram_list) == 0) {
    message("The input list is empty. Returning TRUE as there are no differences.")
    return(TRUE)
  }
  if (length(gram_list) == 1) {
    message("The input list contains only one matrix. Returning TRUE.")
    return(TRUE)
  }

  # Get the first matrix as the reference
  first_matrix <- gram_list[[1]]

  # Ensure the first element is a matrix
  if (!is.matrix(first_matrix)) {
    stop("The first element of 'gram_list' is not a matrix.")
  }

  # Iterate from the second matrix onwards and compare with the first
  for (i in 2:length(gram_list)) {
    current_matrix <- gram_list[[i]]

    # Ensure current element is a matrix
    if (!is.matrix(current_matrix)) {
      stop(paste("Element", i, "of 'gram_list' is not a matrix."))
    }

    # Compare the current matrix with the first matrix
    # all.equal returns TRUE if identical, or a character string describing differences
    # We convert the result to a logical TRUE/FALSE
    if (!isTRUE(all.equal(first_matrix, current_matrix, tolerance = tolerance))) {
      # If not equal, return FALSE immediately
      message(paste("Matrices at index 1 and", i, "are not identical."))
      return(FALSE)
    }
  }

  # If the loop completes, all matrices are identical
  return(TRUE)
}
```

```{r}

# --- Example Usage ---

# Example 1: All matrices are identical
mat1 <- matrix(c(1, 2, 3, 4), nrow = 2)
mat2 <- matrix(c(1, 2, 3, 4), nrow = 2)
mat3 <- matrix(c(1, 2, 3, 4), nrow = 2)
identical_list <- list(mat1, mat2, mat3)
print("Test Case 1: All matrices identical")
print(are_all_gram_matrices_identical(identical_list)) # Expected: TRUE

# Example 2: Matrices with slight floating-point differences (within tolerance)
mat4 <- matrix(c(1.000000000000001, 2, 3, 4), nrow = 2)
mat5 <- matrix(c(1, 2, 3, 4), nrow = 2)
tolerance_list <- list(mat4, mat5)
print("Test Case 2: Matrices with slight floating-point differences")
print(are_all_gram_matrices_identical(tolerance_list)) # Expected: TRUE

# Example 3: Matrices are not identical
mat6 <- matrix(c(1, 2, 3, 5), nrow = 2) # Different value
non_identical_list <- list(mat1, mat6, mat3)
print("Test Case 3: Matrices are not identical")
print(are_all_gram_matrices_identical(non_identical_list)) # Expected: FALSE

# Example 4: List with different dimensions
mat7 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3)
diff_dim_list <- list(mat1, mat7)
print("Test Case 4: Matrices with different dimensions")
print(are_all_gram_matrices_identical(diff_dim_list)) # Expected: FALSE (all.equal will catch this)

# Example 5: Empty list
empty_list <- list()
print("Test Case 5: Empty list")
print(are_all_gram_matrices_identical(empty_list)) # Expected: TRUE

# Example 6: List with a single matrix
single_matrix_list <- list(mat1)
print("Test Case 6: Single matrix list")
print(are_all_gram_matrices_identical(single_matrix_list)) # Expected: TRUE

# Example 7: List containing non-matrix elements (will stop with an error)
# non_matrix_list <- list(mat1, "not a matrix", mat3)
# print("Test Case 7: List with non-matrix element (will throw error)")
# print(are_all_gram_matrices_identical(non_matrix_list))
```
